Resource Use and the Value-Productivity Tradeoff in Australian Winegrowing Regions

### 2023-06-29 article.tex
Fixed referencesgit add article.tex! It is all in the correct review style now.

\documentclass[12pt,australian]{article}
\usepackage{lingmacros}
\usepackage{tree-dvips}
\usepackage[utf8]{inputenc}
\usepackage{csquotes,xpatch}% recommended
\usepackage[australian]{babel}
\usepackage{amsmath}
\usepackage[backend=biber,<options>]{biblatex}
\usepackage{graphicx}
\addbibresource[location=local]{references.bib}

\title{Resource Use and the Value-Productivity Tradeoff in Australian Winegrowing Regions}
\author{Bryce Polley}
\date{20/06/2023}

\begin{document}
\begin{sloppypar}

\section{Introduction}

The global focus on sustainability in agronomic industries has changed the way in which these enterprises do business. When strategies for a sustainable industry are assessed, there is a trade-off between balancing the amount of resources invested and the resultant quality verses quantity of crops produced. This dilemma exists across agriculture, sharing fundemental considerations such as water and nitrogen input \autocite{hemmingCherryTomatoProduction2020,kawasakiQualityMattersMore2016,zhuEffectsNitrogenLevel2017}. Within viticulture (the cultivation of grapes for wine production) quality is driven by its integration within the wine industry; with a wine's potential quality being initially defined through the chemical makeup of the grapes used in its production. The consideration of sustainability is further complicated by environmental and socio-demographic pressures. In the Australian context, these include biosecurity, climate and international market demands.

In this analysis we observe relationships between quantity and quality through the use of linear models. Quality can be defined in a variety of ways for grapes, such as # # #. For the purpose of this study quality was defined by the financial value of grapes per tonne; this was due to varying differences in defining quality between grape varietals.

An extensive amount of research into a variety of factor's effect on grape quality and yield exists. Due to the lack of long-term and in-depth data sources, individual effects are often studied in isolation \autocite{abbalDecisionSupportSystem2016}. The lack of consolidated datasets also restricts the ability to gain statistical insight at a large scale across multiple regions \autocite{keithjonesAustralianWineIndustry2002,knightFirmResourcesDevelopment2019}. The dataset used for this analysis includes data collected for the past 10 years from a multitude of vineyards located over a diverse range of Australian winegrowing regions.

@@

\begin{table}[]
    \begin{center}
      \caption{Summary of models; their predictors, covariates and variable interactions.}
      \label{tab:tab1}
      \begin{tabular}{ccccc}
        & Response & Predictors & Covariates & Interactions \\
        Model 1 & Yield & Water Used, Scope 1 Emissions & Area Harvested, Year, GI Region & N\textbackslash A \\
        Model 2 & ${\text{Yield}}\over{\text{Area Harvested}}$ & Water Used, Scope 1 Emissions & Area Harvested, Year, GI Region & Area Harvested * Scope 1 Emissions, Area Harvested * Water Use, Year * Region \\
        Model 3 & \small{$\text{Yield} {\times} \text{Average Sale Price}$} &  Water Used, Scope 1 Emissions& Area Harvested, Year, GI Region & Area Harvested * Scope 1 Emissions, Area Harvested * Water Use, Year * Region  \\
        Model 4 & ${\text{Yield} \times \text{Average Sale Price}}\over{\text{Area Harvested}}$ & Water Used, Scope 1 Emissions & Area Harvested, Year, GI Region  & N\textbackslash A
      \end{tabular}
    \end{center}
\end{table}

\subsection{Data}
The data used in this analysis was provided by Sustainable Winegrowing Australia, Australia's national wine industry sustainability program. Sustainable winegrowing Australia aims to facilitate grape-growers and winemakers in demonstrating and improving their sustainability \autocite{swaSustainableWingrowingAustralia2022}. Data recorded by Sustainable Winegrowing Australia is entered manually by winegrowers using a web based interface; with some fields being optional. Two subsets of this data were defined by vineyards that recorded values for average price of grape sales per tonne, and vineyards who did not. Both subsets contained: region, harvest year, yield, area harvested, water used and fuel used (in litres for diesel, petrol, biodiesel and LPG). To enable comparisons, total fuel was converted to amount of carbon emissions in metric tons.

@@

Data was limited to samples that had recorded values for variables used (see Table 1). After reviewing correlation coefficients the data was logarithmically transformed, centred and scaled by standard deviation. Two values for average sale price were removed from the dataset, due to a recording of \$1. Unreported values for average prices per tonne were filled in using regional averages taken from Wine Australia's annual reports, where they were available \autocite{wineaustraliaNationalVintageReport2019,wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,wineaustraliaNationalVintageReport2022,winemakersfederationofaustraliaNationalVintageReport2012,winemakersfederationofaustraliaNationalVintageReport2013,winemakersfederationofaustraliaNationalVintageReport2014,winemakersfederationofaustraliaNationalVintageReport2015,winemakersfederationofaustraliaNationalVintageReport2016,winemakersfederationofaustraliaNationalVintageReport2017,winemakersfederationofaustraliaNationalVintageReport2018}.

@@

was used to convert the quantity of fuel in litres, $Q$, using a prescribed Energy Content, $EC$, and emission factors of scope one, $EF1$, and scope three, $EF3$, to tonnes of Carbon Dioxide equivalent, $tCO2e$ \autocite{departmentofclimatechangeenergytheenvironmentandwaterAustralianNationalGreenhouse2022}.

@@

\subsection{Region}
The site of a vineyard predetermines several physical parameters such as climate, geology and soil; making location a widely considered key determinant of grape yield and quality \autocite{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,fragaMultivariateClusteringViticultural2017}. Differences in vineyard locations were captured through the use of Geographical Indicator Regions (GI Regions). Each GI Region has its own unique mixture of climatic and geophsical properties that describes a unique winegrowing region within Australia; these regions were predefined by Wine Australia \autocite{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}.

The climatic properties of a GI Region are summarised in the Sustainable Winegrowing Australia user manual \autocite{swaSustainableWinegrowingAustralia2021}. The user manual describes climates by rainfall and temperature, creating supersets of Regions of similar climatic properties. The climatic groups were used to illustrate similarities and differences occurring in areas larger than GI regions.

@@

Data preprocessing, such as logarithmic transforms, was done using the Python programming language \autocite{g.vanrossumPythonTutorialTechnical1995}. Linear models were created using the R statistical programming language \autocite{rcoreteamLanguageEnvironmentStatistical2021}. These models were created iteratively to explore a variety of variable interactions and approaches to modelling the data. Not all explored approaches yielded improvements or accurate models. Alternate approaches included the use of Splines, hierarchical regression, Additive and Generalised Linear Models. Other variables were also explored but not used due to low reporting values such as fertiliser, tractor and contractor use. The use of only scope one emissions was due to the same reason where scope 2 sources were recorded sporadically at best.

\subsection{Model Validation}
Models were validated using K-fold cross validation calculated through the R Caret Package \autocite{kuhnBuildingPredictiveModels2008}. K-fold cross validation works by removing a subset of data from the sample used to train models and then predicts those variables to determine how sensitive the model is to changes in the sample data. For this analysis each model was validated using 10 folds, repeated 100 times. % A reference for this is absolutely needed.

@@

\begin{table}[]
  \caption{Summary of models, their predictors, covariates and variable interactions.}
  \label{tab:tab2}
  \begin{tabular}{cccccccc}
  Variable                             & Yield      & Area       & Water Used & Scope One Emissions & $\text{Yield}\over\text{Area}$ & Average Price Per Tonne & ${\text{Average Price per tonne}\over\text{Area}}$ \\
  Yield                                & 1.000E+00  & 7.440E-01  & -4.309E-03 & 7.290E-01           & 3.500E-01            & -2.262E-01              & -1.644E-01                           \\
  Area                                 & 7.440E-01  & 1.000E+00  & -5.331E-03 & 8.921E-01           & 7.854E-02            & -1.178E-01              & -2.042E-01                           \\
  Water Used                           & -4.309E-03 & -5.331E-03 & 1.000E+00  & -1.929E-03          & -5.600E-03           & -3.562E-02              & -2.669E-02                           \\
  Scope One Emissions                  & 7.290E-01  & 8.921E-01  & -1.929E-03 & 1.000E+00           & 9.357E-02            & -9.422E-02              & -1.933E-01                           \\
  $\text{Yield}\over\text{Area}$                 & 3.500E-01  & 7.854E-02  & -5.600E-03 & 9.357E-02           & 1.000E+00            & -4.849E-01              & -1.698E-01                           \\
  Average Price Per Tonne              & -2.262E-01 & -1.178E-01 & -3.562E-02 & -9.422E-02          & -4.849E-01           & 1.000E+00               & 4.732E-01                            \\
  ${\text{Average Price per tonne}\over\text{Area}}$ & -1.644E-01 & -2.042E-01 & -2.669E-02 & -1.933E-01          & -1.698E-01           & 4.732E-01               & 1.000E+00                           
  \end{tabular}
  \end{table}

  \begin{table}[]
    \caption{Pearson correlation coefficients for each logarithmically transformed variable.}
    \label{tab:tab3}
    \begin{tabular}{clllllll}
    Variable                                           & \multicolumn{1}{c}{Yield} & \multicolumn{1}{c}{Area} & \multicolumn{1}{c}{Water Used} & \multicolumn{1}{c}{Scope One Emissions} & \multicolumn{1}{c}{$\text{Yield}\over\text{Area}$} & \multicolumn{1}{c}{Average Price Per Tonne} & \multicolumn{1}{c}{${\text{Average Price per tonne}\over\text{Area}}$} \\
    Yield                                              & 1.000E+00                 & 8.822E-01                & 8.245E-01                      & 7.617E-01                               & 9.353E-01                                          & -4.591E-01                                  & -8.918E-01                                                             \\
    Area                                               & 8.822E-01                 & 1.000E+00                & 7.750E-01                      & 8.311E-01                               & 6.742E-01                                          & -1.911E-01                                  & -8.474E-01                                                             \\
    Water Used                                         & 8.245E-01                 & 7.750E-01                & 1.000E+00                      & 6.668E-01                               & 7.292E-01                                          & -4.881E-01                                  & -8.300E-01                                                             \\
    Scope One Emissions                                & 7.617E-01                 & 8.311E-01                & 6.668E-01                      & 1.000E+00                               & 6.086E-01                                          & -1.559E-01                                  & -7.063E-01                                                             \\
    $\text{Yield}\over\text{Area}$                     & 9.353E-01                 & 6.742E-01                & 7.292E-01                      & 6.086E-01                               & 1.000E+00                                          & -5.625E-01                                  & -8.076E-01                                                             \\
    Average Price Per Tonne                            & -4.591E-01                & -1.911E-01               & -4.881E-01                     & -1.559E-01                              & -5.625E-01                                         & 1.000E+00                                   & 6.592E-01                                                              \\
    ${\text{Average Price per tonne}\over\text{Area}}$ & -8.918E-01                & -8.474E-01               & -8.300E-01                     & -7.063E-01                              & -8.076E-01                                         & 6.592E-01                                   & 1.000E+00                                                             
    \end{tabular}
    \end{table}

    \begin{table}[]
      \caption{P-values for the non-transformed water used variable's Pearson correlation coefficients.}
    \label{tab:tab4}
      \begin{tabular}{cl}
      Variable                                           & Water Used \\
      Yield                                              & 7.538E-01  \\
      Area                                               & 6.981E-01  \\
      Scope One Emissions                                & 8.883E-01  \\
      $\text{Yield}\over\text{Area}$                     & 6.836E-01  \\
      Average Price Per Tonne                            & 5.600E-02  \\
      ${\text{Average Price per tonne}\over\text{Area}}$ & 1.522E-01 
      \end{tabular}
      \end{table}

    \begin{table}[]
      \caption{Summary statistics for each variable on the original scale..}
      \label{tab:tab5}
      \begin{tabular}{clllllll}
      Variable &
        \multicolumn{1}{c}{Yield} &
        \multicolumn{1}{c}{Area} &
        \multicolumn{1}{c}{Water Used} &
        \multicolumn{1}{c}{Scope One Emissions} &
        \multicolumn{1}{c}{$\text{Yield}\over\text{Area}$} &
        \multicolumn{1}{c}{Average Price Per Tonne} &
        \multicolumn{1}{c}{${\text{Average Price per tonne}\over\text{Area}}$} \\
      Yield                                              & 1.000E+00  & 8.822E-01  & 8.245E-01  & 7.617E-01  & 9.353E-01  & -4.591E-01 & -8.918E-01 \\
      Area                                               & 8.822E-01  & 1.000E+00  & 7.750E-01  & 8.311E-01  & 6.742E-01  & -1.911E-01 & -8.474E-01 \\
      Water Used                                         & 8.245E-01  & 7.750E-01  & 1.000E+00  & 6.668E-01  & 7.292E-01  & -4.881E-01 & -8.300E-01 \\
      Scope One Emissions                                & 7.617E-01  & 8.311E-01  & 6.668E-01  & 1.000E+00  & 6.086E-01  & -1.559E-01 & -7.063E-01 \\
      $\text{Yield}\over\text{Area}$                     & 9.353E-01  & 6.742E-01  & 7.292E-01  & 6.086E-01  & 1.000E+00  & -5.625E-01 & -8.076E-01 \\
      Average Price Per Tonne                            & -4.591E-01 & -1.911E-01 & -4.881E-01 & -1.559E-01 & -5.625E-01 & 1.000E+00  & 6.592E-01  \\
      ${\text{Average Price per tonne}\over\text{Area}}$ & -8.918E-01 & -8.474E-01 & -8.300E-01 & -7.063E-01 & -8.076E-01 & 6.592E-01  & 1.000E+00 
      \end{tabular}
      \end{table}

@@

\section{Discussion}
% this needs serious revision.
This study investigated the general relationships between input resources of a vineyard, including fuel and water, and the outputs including yield and value. Some regions appeared to produce many low quality grapes at scale compared to attempting to produce fewer higher quality grapes. This behaviour can be observed when reviewing Wine Australia’s annual reports, where it is apparent that warm inland regions such as the Riverland are known to only produce large amounts of lower graded grapes \autocite{wineaustraliaNationalVintageReport2022,winemakersfederationofaustraliaNationalVintageReport2017}. Comparatively, regions such as Tasmania only produce A grade grapes but in much smaller quantities than the Riverland. Knowing that the difference in pricing per tonne can exceed a magnitude of 10 between grades E and A, the operations in regions that target different grades would have varied priorities. However, some regions such as the Yarra Valley produce a Variety of different grades of grapes, from C to A, highlighting that vineyard priorities, although may be somewhat present within regional classifications, are not necessarily aligned within a given region.

The opportunity to target different grades of grapes may not always be available, with some regions being more renowned than others, and likely to be sought after regardless \autocite{hallidayAustralianWineEncyclopedia2009}. The Barossa is an example of this, known for its quality could also lend itself to a bias in purchasers not considering other regions that may be capable of similar quality. This effect could stifle the potential for market opportunities within these lesser known regions. A further possibility is that there may be regional upper limits with the relationship between resource input and the value gained becoming no longer proportional due to diminishing returns. Climate was considered to be a large determinant of the ability to grow a larger quantity of grapes, as well as a determinant in grape quality \autocite{agostaRegionalClimateVariability2012}; however there were vineyards in similar regions that were able to produce exceptionally better results than others (See Figure 7).

@@

\printbibliography{}
\end{sloppypar}
\end{document}

>>>>

%% 
%% Copyright 2007-2020 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%% 
%% Template article for Elsevier's document class `elsarticle'
%% with harvard style bibliographic references

\documentclass[review,12pt,authoryear]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times,authoryear]{elsarticle}
%% \documentclass[final,1p,times,twocolumn,authoryear]{elsarticle}
%% \documentclass[final,3p,times,authoryear]{elsarticle}
%% \documentclass[final,3p,times,twocolumn,authoryear]{elsarticle}
%% \documentclass[final,5p,times,authoryear]{elsarticle}
%% \documentclass[final,5p,times,twocolumn,authoryear]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
\usepackage{lineno}

\journal{Geography and Sustainability}

\begin{document}
\begin{linenumbers}
\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \affiliation for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \affiliation{organization={},
%%            addressline={}, 
%%            city={},
%%            postcode={}, 
%%            state={},
%%            country={}}
%% \fntext[label3]{}

    \title{Resource Use and the Value-Productivity Tradeoff in Australian Winegrowing Regions}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \affiliation[label1]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%%
%% \affiliation[label2]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}

    \affiliation[label1]{organization={QUT},
                 addressline={},
                 city={},
                 postcode={},
                 state={QLD},
                 country={}}
    \affiliation[label2]{organization={AWRI},
                 addressline={},
                 city={},
                 postcode={},
                 state={SA},
                 country={}}
    \affiliation[label3]{organization={Food Agility CRC},
                 addressline={},
                 city={},
                 postcode={},
                 state={Vic},
                 country={}}
\author[label1,label2,label3]{Bryce Polley}
\date{20/06/2023}

    \begin{abstract}
      %% Text of abstract
      Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
      \end{abstract}

      %%Graphical abstract
      \begin{graphicalabstract}
        \includegraphics{graphical_abstract.jpeg}
      \end{graphicalabstract}

      \begin{keyword}
      %% keywords here, in the form: keyword \sep keyword
      keyword one \sep keyword two
      %% PACS codes here, in the form: \PACS code \sep code
      \PACS 0000 \sep 1111
      %% MSC codes here, in the form: \MSC code \sep code
      %% or \MSC[2008] code \sep code (2000 is the default)
      \MSC 0000 \sep 1111
      \end{keyword}

      %%Research highlights
      \begin{highlights}
        \item Research highlight 1
        \item Research highlight 2
        \end{highlights}

      \end{frontmatter}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                main text             %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
The global focus on sustainability in agronomic industries has changed the way in which these enterprises do business. When strategies for a sustainable industry are assessed, there is a trade-off between balancing the amount of resources invested and the resultant quality verses quantity of crops produced. This dilemma exists across agriculture, sharing fundemental considerations such as water and nitrogen input 
\citep{abadCoverCropsViticulture2021}

\cite{hemmingCherryTomatoProduction2020,kawasakiQualityMattersMore2016, zhuEffectsNitrogenLevel2017}. 
\citet{hemmingCherryTomatoProduction2020,kawasakiQualityMattersMore2016, zhuEffectsNitrogenLevel2017}.

Within viticulture (the cultivation of grapes for wine production) quality is driven by its integration within the wine industry; with a wine's potential quality being initially defined through the chemical makeup of the grapes used in its production. The consideration of sustainability is further complicated by environmental and socio-demographic pressures. In the Australian context, these include biosecurity, climate and international market demands.

In this analysis we observe relationships between quantity and quality through the use of linear models. Quality can be defined in a variety of ways for grapes, such as *. For the purpose of this study quality was defined by the financial value of grapes per tonne; this was due to varying differences in defining quality between grape varietals.

An extensive amount of research into a variety of factor's effect on grape quality and yield exists. Due to the lack of long-term and in-depth data sources, individual effects are often studied in isolation \citep{abbalDecisionSupportSystem2016}. The lack of consolidated datasets also restricts the ability to gain statistical insight at a large scale across multiple regions \citep{keithjonesAustralianWineIndustry2002,knightFirmResourcesDevelopment2019}. The dataset used for this analysis includes data collected for the past 10 years from a multitude of vineyards located over a diverse range of Australian winegrowing regions.

@@

\begin{table}[]
    \begin{center}
      \caption{Summary of models; their predictors, covariates and variable interactions.}
      \label{tab:tab1}
      \begin{tabular}{ccccc}
        & Response & Predictors & Covariates & Interactions \\
        Model 1 & Yield & Water Used, Scope 1 Emissions & Area Harvested, Year, GI Region & N\textbackslash A \\
        Model 2 & ${ \textrm{Yield}}\over{ \textrm{Area Harvested}}$ & Water Used, Scope 1 Emissions & Area Harvested, Year, GI Region & Area Harvested * Scope 1 Emissions, Area Harvested * Water Use, Year * Region \\
        Model 3 & \small{$\textrm{Yield} {\times} \textrm{Average Sale Price}$} &  Water Used, Scope 1 Emissions& Area Harvested, Year, GI Region & Area Harvested * Scope 1 Emissions, Area Harvested * Water Use, Year * Region  \\
        Model 4 & ${\textrm{Yield} \times \textrm{Average Sale Price}}\over{\textrm{Area Harvested}}$ & Water Used, Scope 1 Emissions & Area Harvested, Year, GI Region  & N\textbackslash A
      \end{tabular}
    \end{center}
\end{table}

\subsection{Data}
The data used in this analysis was provided by Sustainable Winegrowing Australia, Australia's national wine industry sustainability program. Sustainable winegrowing Australia aims to facilitate grape-growers and winemakers in demonstrating and improving their sustainability \citep{swaSustainableWingrowingAustralia2022}. Data recorded by Sustainable Winegrowing Australia is entered manually by winegrowers using a web based interface; with some fields being optional. Two subsets of this data were defined by vineyards that recorded values for average price of grape sales per tonne, and vineyards who did not. Both subsets contained: region, harvest year, yield, area harvested, water used and fuel used (in litres for diesel, petrol, biodiesel and LPG). To enable comparisons, total fuel was converted to amount of carbon emissions in metric tons.

@@

Data was limited to samples that had recorded values for variables used (see Table 1). After reviewing correlation coefficients the data was logarithmically transformed, centred and scaled by standard deviation. Two values for average sale price were removed from the dataset, due to a recording of \$1. Unreported values for average prices per tonne were filled in using regional averages taken from Wine Australia's annual reports, where they were available \citep{wineaustraliaNationalVintageReport2019,wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,wineaustraliaNationalVintageReport2022,winemakersfederationofaustraliaNationalVintageReport2012,winemakersfederationofaustraliaNationalVintageReport2013,winemakersfederationofaustraliaNationalVintageReport2014,winemakersfederationofaustraliaNationalVintageReport2015,winemakersfederationofaustraliaNationalVintageReport2016,winemakersfederationofaustraliaNationalVintageReport2017,winemakersfederationofaustraliaNationalVintageReport2018}.

@@

was used to convert the quantity of fuel in litres, $Q$, using a prescribed Energy Content, $EC$, and emission factors of scope one, $EF1$, and scope three, $EF3$, to tonnes of Carbon Dioxide equivalent, $tCO2e$ \citep{departmentofclimatechangeenergytheenvironmentandwaterAustralianNationalGreenhouse2022}.

@@

\subsection{Region}
The site of a vineyard predetermines several physical parameters such as climate, geology and soil; making location a widely considered key determinant of grape yield and quality \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,fragaMultivariateClusteringViticultural2017}. Differences in vineyard locations were captured through the use of Geographical Indicator Regions (GI Regions). Each GI Region has its own unique mixture of climatic and geophsical properties that describes a unique winegrowing region within Australia; these regions were predefined by Wine Australia \citep{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}.

The climatic properties of a GI Region are summarised in the Sustainable Winegrowing Australia user manual \citep{swaSustainableWinegrowingAustralia2021}. The user manual describes climates by rainfall and temperature, creating supersets of Regions of similar climatic properties. The climatic groups were used to illustrate similarities and differences occurring in areas larger than GI regions.

@@

Data preprocessing, such as logarithmic transforms, was done using the Python programming language \citep{g.vanrossumPythonTutorialTechnical1995}. Linear models were created using the R statistical programming language \citep{rcoreteamLanguageEnvironmentStatistical2021}. These models were created iteratively to explore a variety of variable interactions and approaches to modelling the data. Not all explored approaches yielded improvements or accurate models. Alternate approaches included the use of Splines, hierarchical regression, Additive and Generalised Linear Models. Other variables were also explored but not used due to low reporting values such as fertiliser, tractor and contractor use. The use of only scope one emissions was due to the same reason where scope 2 sources were recorded sporadically at best.

\subsection{Model Validation}
Models were validated using K-fold cross validation calculated through the R Caret Package \citep{kuhnBuildingPredictiveModels2008}. K-fold cross validation works by removing a subset of data from the sample used to train models and then predicts those variables to determine how sensitive the model is to changes in the sample data. For this analysis each model was validated using 10 folds, repeated 100 times. % A reference for this is absolutely needed.

@@

\begin{table}[]
  \caption{Summary of models, their predictors, covariates and variable interactions.}
  \label{tab:tab2}
  \begin{tabular}{cccccccc}
  Variable                             & Yield      & Area       & Water Used & Scope One Emissions & $\textrm{Yield}\over\textrm{Area}$ & Average Price Per Tonne & ${\textrm{Average Price per tonne}\over\textrm{Area}}$ \\
  Yield                                & 1.000E+00  & 7.440E-01  & -4.309E-03 & 7.290E-01           & 3.500E-01            & -2.262E-01              & -1.644E-01                           \\
  Area                                 & 7.440E-01  & 1.000E+00  & -5.331E-03 & 8.921E-01           & 7.854E-02            & -1.178E-01              & -2.042E-01                           \\
  Water Used                           & -4.309E-03 & -5.331E-03 & 1.000E+00  & -1.929E-03          & -5.600E-03           & -3.562E-02              & -2.669E-02                           \\
  Scope One Emissions                  & 7.290E-01  & 8.921E-01  & -1.929E-03 & 1.000E+00           & 9.357E-02            & -9.422E-02              & -1.933E-01                           \\
  $\textrm{Yield}\over\textrm{Area}$                 & 3.500E-01  & 7.854E-02  & -5.600E-03 & 9.357E-02           & 1.000E+00            & -4.849E-01              & -1.698E-01                           \\
  Average Price Per Tonne              & -2.262E-01 & -1.178E-01 & -3.562E-02 & -9.422E-02          & -4.849E-01           & 1.000E+00               & 4.732E-01                            \\
  ${\textrm{Average Price per tonne}\over\textrm{Area}}$ & -1.644E-01 & -2.042E-01 & -2.669E-02 & -1.933E-01          & -1.698E-01           & 4.732E-01               & 1.000E+00                           
  \end{tabular}
  \end{table}

  \begin{table}[]
    \caption{Pearson correlation coefficients for each logarithmically transformed variable.}
    \label{tab:tab3}
    \begin{tabular}{clllllll}
    Variable                                           & \multicolumn{1}{c}{Yield} & \multicolumn{1}{c}{Area} & \multicolumn{1}{c}{Water Used} & \multicolumn{1}{c}{Scope One Emissions} & \multicolumn{1}{c}{$\textrm{Yield}\over\textrm{Area}$} & \multicolumn{1}{c}{Average Price Per Tonne} & \multicolumn{1}{c}{${\textrm{Average Price per tonne}\over\textrm{Area}}$} \\
    Yield                                              & 1.000E+00                 & 8.822E-01                & 8.245E-01                      & 7.617E-01                               & 9.353E-01                                          & -4.591E-01                                  & -8.918E-01                                                             \\
    Area                                               & 8.822E-01                 & 1.000E+00                & 7.750E-01                      & 8.311E-01                               & 6.742E-01                                          & -1.911E-01                                  & -8.474E-01                                                             \\
    Water Used                                         & 8.245E-01                 & 7.750E-01                & 1.000E+00                      & 6.668E-01                               & 7.292E-01                                          & -4.881E-01                                  & -8.300E-01                                                             \\
    Scope One Emissions                                & 7.617E-01                 & 8.311E-01                & 6.668E-01                      & 1.000E+00                               & 6.086E-01                                          & -1.559E-01                                  & -7.063E-01                                                             \\
    $\textrm{Yield}\over\textrm{Area}$                     & 9.353E-01                 & 6.742E-01                & 7.292E-01                      & 6.086E-01                               & 1.000E+00                                          & -5.625E-01                                  & -8.076E-01                                                             \\
    Average Price Per Tonne                            & -4.591E-01                & -1.911E-01               & -4.881E-01                     & -1.559E-01                              & -5.625E-01                                         & 1.000E+00                                   & 6.592E-01                                                              \\
    ${\textrm{Average Price per tonne}\over\textrm{Area}}$ & -8.918E-01                & -8.474E-01               & -8.300E-01                     & -7.063E-01                              & -8.076E-01                                         & 6.592E-01                                   & 1.000E+00                                                             
    \end{tabular}
    \end{table}

    \begin{table}[]
      \caption{P-values for the non-transformed water used variable's Pearson correlation coefficients.}
    \label{tab:tab4}
      \begin{tabular}{cl}
      Variable                                           & Water Used \\
      Yield                                              & 7.538E-01  \\
      Area                                               & 6.981E-01  \\
      Scope One Emissions                                & 8.883E-01  \\
      $\textrm{Yield}\over\textrm{Area}$                     & 6.836E-01  \\
      Average Price Per Tonne                            & 5.600E-02  \\
      ${\textrm{Average Price per tonne}\over\textrm{Area}}$ & 1.522E-01 
      \end{tabular}
      \end{table}

    \begin{table}[]
      \caption{Summary statistics for each variable on the original scale..}
      \label{tab:tab5}
      \begin{tabular}{clllllll}
      Variable &
        \multicolumn{1}{c}{Yield} &
        \multicolumn{1}{c}{Area} &
        \multicolumn{1}{c}{Water Used} &
        \multicolumn{1}{c}{Scope One Emissions} &
        \multicolumn{1}{c}{$\textrm{Yield}\over\textrm{Area}$} &
        \multicolumn{1}{c}{Average Price Per Tonne} &
        \multicolumn{1}{c}{${\textrm{Average Price per tonne}\over\textrm{Area}}$} \\
      Yield                                              & 1.000E+00  & 8.822E-01  & 8.245E-01  & 7.617E-01  & 9.353E-01  & -4.591E-01 & -8.918E-01 \\
      Area                                               & 8.822E-01  & 1.000E+00  & 7.750E-01  & 8.311E-01  & 6.742E-01  & -1.911E-01 & -8.474E-01 \\
      Water Used                                         & 8.245E-01  & 7.750E-01  & 1.000E+00  & 6.668E-01  & 7.292E-01  & -4.881E-01 & -8.300E-01 \\
      Scope One Emissions                                & 7.617E-01  & 8.311E-01  & 6.668E-01  & 1.000E+00  & 6.086E-01  & -1.559E-01 & -7.063E-01 \\
      $\textrm{Yield}\over\textrm{Area}$                     & 9.353E-01  & 6.742E-01  & 7.292E-01  & 6.086E-01  & 1.000E+00  & -5.625E-01 & -8.076E-01 \\
      Average Price Per Tonne                            & -4.591E-01 & -1.911E-01 & -4.881E-01 & -1.559E-01 & -5.625E-01 & 1.000E+00  & 6.592E-01  \\
      ${\textrm{Average Price per tonne}\over\textrm{Area}}$ & -8.918E-01 & -8.474E-01 & -8.300E-01 & -7.063E-01 & -8.076E-01 & 6.592E-01  & 1.000E+00 
      \end{tabular}
      \end{table}

@@

\section{Discussion}
% this needs serious revision.
This study investigated the general relationships between input resources of a vineyard, including fuel and water, and the outputs including yield and value. Some regions appeared to produce many low quality grapes at scale compared to attempting to produce fewer higher quality grapes. This behaviour can be observed when reviewing Wine Australia’s annual reports, where it is apparent that warm inland regions such as the Riverland are known to only produce large amounts of lower graded grapes \cite{wineaustraliaNationalVintageReport2022,winemakersfederationofaustraliaNationalVintageReport2017}. Comparatively, regions such as Tasmania only produce A grade grapes but in much smaller quantities than the Riverland. Knowing that the difference in pricing per tonne can exceed a magnitude of 10 between grades E and A, the operations in regions that target different grades would have varied priorities. However, some regions such as the Yarra Valley produce a Variety of different grades of grapes, from C to A, highlighting that vineyard priorities, although may be somewhat present within regional classifications, are not necessarily aligned within a given region.

The opportunity to target different grades of grapes may not always be available, with some regions being more renowned than others, and likely to be sought after regardless \citep{hallidayAustralianWineEncyclopedia2009}. The Barossa is an example of this, known for its quality could also lend itself to a bias in purchasers not considering other regions that may be capable of similar quality. This effect could stifle the potential for market opportunities within these lesser known regions. A further possibility is that there may be regional upper limits with the relationship between resource input and the value gained becoming no longer proportional due to diminishing returns. Climate was considered to be a large determinant of the ability to grow a larger quantity of grapes, as well as a determinant in grape quality \citep{agostaRegionalClimateVariability2012}; however there were vineyards in similar regions that were able to produce exceptionally better results than others (See Figure 7).

@@

\bibliography{references}
\bibliographystyle{elsarticle-harv}

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%

%% else use the following coding to input the bibitems directly in the
%% TeX file.

\end{linenumbers}
  \end{document}

  \endinput
